%-------------------------
% Author : Muhammad Gill
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%%%%  Resume %%%%%%%%%%%%%%%%

\begin{document}

%---- info -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{ }{\Large Muhammad Gill}} & \href{ }{ } \\
\href{mailto:mhgill@uwaterloo.ca}{mhgill@uwaterloo.ca} & \href{ }{ } \\
  & \href{ }{ } \\

\end{tabular*}

%---- education -----
\section{education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Waterloo}{Waterloo, ON}{Computer Engineering (Bachelors)}{Class of 2016}
\resumeSubHeadingListEnd

%---- experience -----
\section{experience}
\resumeSubHeadingListStart

\resumeSubheading
{Doordash}{Mountain View, California, USA}{Software Developer}{2021 - Present}
\resumeItemListStart
\item {Designed and wrote logic for a large photo-processing distributed system which currently processes, stores, caches, and serves thousands of merchant photos per second.}
\item {Designed and built AI software to incorporate metrics into extremely large production services. This AI system wrote over 25,000 lines of code that are currently being used in customer-facing production services serving over 20 million users.}
\resumeItemListEnd

\resumeSubheading
{Google}{Mountain View, California, USA}{Software Engineer}{2019 - 2020}
\resumeItemListStart
\item {Wrote a parallel data processing pipeline (c++) to generate text datasets to be used for training almost any Ontology classification model.}
\item {Optimized SQL queries to run on Google's parallel query engine, reducing runtime by 80\%.}
\item {Modified a BERT transformer architecture (python, tensorflow) to be used with an MLP in order to classify text post-encoding, increasing base classification accuracy by over 6\%.}
\item {Achieved state-of-the-art precision classifying wikipedia text, using a modified transformer model.}
\item {Pretrained a BERT encoder (tensorflow) on large volumes of english text using cutting edge parallel TPU technology and kubernetes to achieve over 95\% accuracy on dataset sequences.}
\item {Authored a research paper (publication): Text Object Ontology, in which I present state of the art results in Ontological Text Classification.}
\item {Wrote, and deployed (using kubernetes) a parallel label propagation algorithm (c++) to label unlabelled data samples, increasing algorithm runtime speed by 1800\%, over single machine speed.}
\item {Independently designed and implemented semi-supervised learning pipeline (tensorflow, cpp) for large security datasets. Initial, unoptimized models realized accuracy and F1 scores above 98\%.}
\item {Wrote custom evaluation binary (python, cpp, javascript) to score the semi-supervised and unsupervised models, saving 100s of manual hours.}
\item {Wrote a custom node transformation binary (c++, python) to generate new datasets capable of key-shifting to create 30+ unique label datasets.}
\resumeItemListEnd

\resumeSubheading
{Blackberry LTD}{Waterloo, Ontario, Canada}{Software Developer}{2018}
\resumeItemListStart
\item {Developed deep learning model for relational database syntax conversion from PL/SQL (oracle) to mySQL (100\% precision).}
\item {Developed and optimized dynamic scripts (Java) to efficiently and securely migrate over 20\% of company databases (schema, procedures and data) between different, incompatible platforms.}
\item {Contributed greatly to many other confidential projects (java, javascript, HTML).}
\resumeItemListEnd

\resumeSubheading
{Nielsen Inc}{Markham, Ontario, Canada}{Software Engineer}{2017}
\resumeItemListStart
\item {Wrote data service to process thousands of consumer purchase receipts using open source OCR libraries (saved company thousands of manual hours).}
\item {Customized, optimized an open source mySQL DB (mariaDB) to increase insert speed by 12\%.}
\resumeItemListEnd

\resumeSubheading
{Personal Projects}{}{Software Developer}{2012 - 2017}
\resumeItemListStart
\item {Wrote a model (python) to accurately predict stock price volatility using financial derivative (options) flow having over 82\% 3-day accuracy.}
\item {Independently developed (c++) 3200+ elo chess engine (neural network). Trained using a self generated dataset (90+ million unique chess positions).}
\resumeItemListEnd

\resumeSubHeadingListEnd

%---- skills -----
\section{skills}
\resumeSubHeadingListStart
\resumeSubItem{Operating Systems}
{Linux (Debian/Ubuntu), macOS, Windows}
\resumeSubItem{Languages}
{C++, Python, Java, SQL, Bash, Javascript, CSS, HTML}
\resumeSubItem{Technologies}
{Tensorflow, scikit learn, Pytorch, kubernetes, .NET, Node.js, MATLAB, Express.js}
\resumeSubItem{Tools}
{Git, XCode, Visual Studio, Eclipse, VS Code, Azure, mySQL, mariaDB, MongoDB, AWS, NoSQL}
\resumeSubHeadingListEnd

%---------------END-------------------
\end{document}
